hormones

### 2020-01-14 analysis/07_hormones.Rmd
cort hormones

```{r setup}
library(tidyverse)
library(cowplot)
library(readxl)
library(modelr)
library(lubridate)
library(ggsignif)

@@

>>>>

```{r setup}
library(tidyverse)
library(cowplot)
library(readxl)
library(modelr)
library(lubridate)
library(ggsignif)
library(apaTables)

@@

```{r sex}
hormones$hormone <- factor(hormones$hormone, 
                           levels = c("cort", "progesterone", "prolactin", 
                                      "estradiol", "testosterone"))

hormones %>%
  filter(study == "characterization") %>%
  ggplot(aes(x = sex, y = plasma_conc, fill = sex)) +
  geom_boxplot() +
  theme_B3() +
  facet_wrap(~hormone, nrow = 1, scales = "free") +
  theme(legend.position = "none") +
  labs(y = "concentration (ng/mL")

printaovtablesex <- function(myhormone, mydescirption){

  aov_all = data.frame()
  for(i in alllevels3){
    df <- hormones %>% filter(hormone == myhormone,
                            treatment == i) %>% droplevels()
    aovtable <- apa.aov.table(aov(plasma_conc ~ sex, data  = df))
    aovtable <- as.data.frame(aovtable$table_body)
    totaldf <- aovtable[3, 3]
    aovtable$df <- paste(aovtable$df, ", " , totaldf, sep = "")
    aovtable$ANOVA <- mydescirption
    aovtable$stages <- paste(i)
    aovtable$p <- as.numeric(as.character(aovtable$p))
    aov_all <- rbind(aov_all,aovtable)
  }

  aov_all <- aov_all %>%
    filter(Predictor == "sex")  %>%
    select(stages, ANOVA, df, "F", p) %>%
    mutate(sig = ifelse(p < 0.05, "*", " "))
  aov_all
  return(aov_all)
}

printaovtablesex("cort", "CORT ~ sex")
printaovtablesex("progesterone", "Prog ~ sex")
printaovtablesex("prolactin", "PRL ~ sex")

TukeyHSD(aov(data = cort.char, plasma_conc ~ treatment), which = "treatment")

```{r cort}
p1 <- hormones %>%
  filter(hormone == "cort",
         study == "characterization") %>%
  ggplot(aes(x = sex, y = plasma_conc, fill = sex)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = "concentration (ng/mL)", subtitle = "Corticosterone" , x = NULL) +
  theme(legend.position = "none") +
  scale_y_continuous(limits = c(0,8.5))
p1

cort <- hormones %>%
  filter(hormone == "cort",
         study == "characterization")

p2 <-  ggplot(cort, aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = NULL, x = NULL, subtitle = " ") +
  theme(legend.position = "none") +
  geom_signif(comparisons=list(c("control", "inc.d17")), annotations= "p = 0.49", y_position = 7.5, tip_length = 0, vjust = 0, color= "black" , textsize = 3 ) +
  geom_signif(comparisons=list(c("control", "hatch")), annotations= "p = 0.021", y_position = 8, tip_length = 0, vjust = 0, color= "black" , textsize = 3 ) +
  geom_signif(comparisons=list(c("control", "n5")), annotations= "p = 0.004", y_position = 8.5, tip_length = 0, vjust = 0, color= "black" , textsize = 3 ) +
  geom_signif(comparisons=list(c("n5", "n9")), annotations= "p = 0.001", y_position = 8, tip_length = 0, vjust = 0, color= "black" , textsize = 3 ) +
  scale_y_continuous(limits = c(0,8.5))

p2

p12 <- plot_grid(p1,p2, rel_widths = c(0.2,0.8))

p3 <- hormones %>%
  filter(hormone == "cort",
         treatment %in% c(controlsremoval, levelsremoval )) %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot() +
  theme_B3() +
  scale_y_continuous(limits = c(0,8.5)) +
  scale_fill_manual(values = colorscharmaip) +
  theme(legend.position = "none") +
  labs( x = NULL, y = "concentration (ng/mL")
p3

p4 <- hormones %>%
  filter(hormone == "cort",
         treatment %in% c(controlstiming, levelstiming )) %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot() +
  theme_B3() +
  scale_y_continuous(limits = c(0,8.5)) +
  scale_fill_manual(values = colorscharmaip) +
  theme(legend.position = "none") +
  labs(y = NULL, x = NULL)
p4

p34 <- plot_grid(p3,p4, rel_widths = c(0.6,0.4))

plot_grid(p12, p34, nrow = 2, rel_heights = c(0.6,0.4))
```
